\documentclass[oneside]{book}

\usepackage{Style/Master}
\usepackage{Style/boxes}
\usepackage{Style/DefNoteFact}
\usepackage{Style/QnsProof}
\usepackage{Style/Thms}
\usepackage{Style/Env}

\begin{document}

\input{Titlepage.tex}

\chapter{A1: Inequalities and Equations}
\section{Solving Inequalities}
\subsection{Rational Inequalities}
\begin{stbox}{General Methods}
  \begin{enumerate}
    \item Quadratic formula for factorisation / finding roots (of polynomial).
    \item Completing the square.
    \item Discriminant/Completing the Sq to eliminate{\hyperlink{INEQGM3}{*}} factors which are \emph{always} positive or negative (e.g. removing \(x^2-3x+4\)). \emph{Note to include coefficient of \(x^2\) in argument.}
    \item GC (include sketch).
    \item \emph{Rational Functions}\footnote{Fractions of Polynomials}: Move everything to one side (\(+\),\(-\)), then use number line.
    \item Number line (more complicated functions).
\end{enumerate}
\end{stbox}
\begin{IN}
    \begin{itemize}[label=\footnotesize \(\square\) \normalsize]
        \item \hypertarget{INEQGM3}{Eliminating Factors --- \emph{only}\footnote{Counterexample: \(P(x)=x(3x^2-9x+10) \leq 2\) iff \(x \leq 2\) is false. E.g.: \(P(1.8)=6.336 \not\leq 2\).} works for \(c=0\) in \(f(x) \geq c\) or \(f(x) \leq c\).}
        \item Discriminant --- include coefficient of \(x^2\) in argument.
        \item Rational functions --- exclude the values that causes division by zero to occur. 
        \item Cross multiplication preserves order for \(\frac{x}{y}<\frac{x'}{y'}\) iff \(y\) and \(y'\) are \emph{both} positive or negative.\footnote{Otherwise, note the counterexample \(\frac{1}{2}<\frac{1}{-3}\).}
        \item Squaring preserves order for \(x<y\) iff \(x\) and \(y\) are \emph{both} positive or negative.
    \end{itemize}
\end{IN}
\section{Modulus Inequalities}
\begin{fact}
    Given \(x \in \mathbb{R}\), we have that 
    \begin{itemize}
        \item \(\lvert x \rvert \geq 0\),
        \item \(\lvert x^2 \rvert=\lvert x \rvert^2=x^2\),
        \item \(\sqrt{x^2}=\lvert x \rvert\).
    \end{itemize}
    And as long as \(x \in \mathbb{R}^+\),
    \begin{itemize}
        \item \(\sqrt{x}^2=\lvert x \rvert\).
    \end{itemize}
\end{fact}
\begin{stbox}{Useful Properties}
  For every \(x,k \in \mathbb{R}\):
  \begin{enumerate}[label=(\alph*)]
      \item \(\lvert x \rvert < k\) iff\footnote{Notice that \(k>0\) here since \(0 \leq \lvert x \rvert < k\).} \(-k<x<k\).
      \item \(\lvert x \rvert > k\) iff \(x<-k\) or \(x>k\).
  \end{enumerate}
  \footnotesize (of course, similarly applies for the non-strict ordering \(\leq\)) \normalsize
\end{stbox}
\begin{IN}
    \begin{itemize}[label=\(\circ\)]
        \item Note that when solving for \(\lvert x \rvert=y\), \(\lvert x \rvert < y\), etc, \(y\) must be greater than or equal to 0. In other words, there may be solutions we will need to reject.\\ \footnotesize(For \(<\), equality is of course not allowed.)\normalsize  
    \end{itemize}
\end{IN}
\begin{IN}
\begin{itemize}[label=\scriptsize\(\triangle\)\normalsize]
  \item Carelessness: Look at the question carefully! If they ask for a \emph{set} of values, then rmb to give it as a \emph{set}!
  \item Exponentiation and Logarithms: Simply use \(\ln\) and avoid \(\log_c\) for \(c<1\).\footnote{Order is \emph{Preserved} under exponentiation/logarithms if the base is \emph{larger than} one. Otherwise, when it is \emph{less than} one, the order is \emph{reversed}. \url{https://www.desmos.com/calculator/gd8z5fa0bg}}
\end{itemize}
\end{IN}

\chapter{B1(A): Graphing Techniques (Part I)}
\begin{stbox}{General Definitions}
  \begin{enumerate}
    \item \textbf{Lines of Symmetry}: A \emph{line of symmetry} of a function is a line, such that the function is a reflection of itself about that line.
    \item \textbf{Horizontal Asymptotes}: A (horizontal) line \(g(x)=c\) is the \emph{horizontal asymptote} of the curve \(f(x)\) iff \(\lim_{x \to \infty}{f(x)}=c\) (or with \(-\infty\) instead of \(\infty\)).\footnote{Otherwise notated by \(f(x) \to c\) as \(x \to \infty\).}
    \item \textbf{Vertical Asymptotes}: A (vertical) line \(x=c\) is a \emph{vertical asymptote} of the curve \(f(x)\) iff \(\lim_{x \to c}{f(x)}=\operatorname{\infty} \text{ or } -\infty\).
    \item \textbf{Oblique Asymptotes}: A line \(g(x)=mx+c\) --- where \(m \neq 0\) --- is an \emph{oblique asymptote} of the curve \(f(x)\) iff \(\lim_{x \to \infty}[f(x)-g(x)]=0\) (or with \(-\infty\) instead of \(\infty\)).
\end{enumerate}
\end{stbox}
\begin{stbox}{Curve Sketching (Rational Funcs)}
  \begin{enumerate}
    \item[\textbf{S}] Stationary points
    \item[\textbf{I}] Intersection with axes
    \item[\textbf{A}] Asymptotes   
  \end{enumerate}
  \begin{enumerate}[label=\roman*]
    \item Know how to sketch the graphs of \(y=\frac{ax+b}{cx+d}\) and \(y=\frac{ax^2+bx+c}{dx+e}\).
    \item Rectangular Hyperbolas (of the form \(y=\frac{ax+b}{cx+d}\)):
    \begin{itemize}
      \item \emph{Two} asymptotes, namely \(x=-\frac{d}{c}\) and \(y=\frac{a}{c}\).
      \item \emph{Two} lines of symmetry with gradients \(\pm 1\) \emph{and} pass through the intersection point of the aforementioned two asymptotes.
    \end{itemize}
    \item \emph{If} \(n=\operatorname{deg}P=\operatorname{deg}Q\), then
    \begin{itemize}
      \item \(y=R(x)\) is the \emph{horizontal} asymptote of \(\frac{P(x)}{Q(x)}=R(x)+\frac{S(x)}{Q(x)}\).
      \item Equivalently, \(y=\frac{\operatorname{coeff}_P(x^n)}{\operatorname{coeff}_Q(x^n)}\) is a \emph{horizontal} asymptote.\footnote{E.g.: \(y=\frac{1}{15}\) is a horizontal asymptote of \(y=\frac{\text{\hly{\(1\)}}x^2+2x-3}{(\text{\hly{\(5\)}}x+1)(\text{\hly{\(3\)}}x+2)}\).}
    \end{itemize}
    \item If \(\operatorname{deg}P=\operatorname{deg}Q+1\), then \(R(x)\) is an \emph{oblique} asymptote of \(\frac{P(x)}{Q(x)}=R(x)+\frac{S(x)}{Q(x)}\).
    \item Write down asymptotes and lines of symmetry.\footnote{E.g.: \begin{itemize}
      \item[] Asymptotes: \(x=4\), \(y=20\).
      \item[] Lines of Symmetry: \(y=x+16\), \(y=-x+24\).
    \end{itemize} } If none are present indicate with ``No lines of symmetry.''
  \end{enumerate}
\end{stbox}

\end{document}